European or American? A re-examination of the transatlantic influence over the IMF

### 2025-04-22 manuscript/dissertation.tex
share csl and bib

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[top=30mm,left=30mm,right=30mm,heightrounded]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

% TODO: Add custom LaTeX header directives here
\usepackage{float, booktabs, siunitx, orcidlink}
\setkomafont{disposition}{\bfseries}
\providecommand{\keywords}[1]
{
  \small	
  \textbf
{\textit{Keywords---}} #1
}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={European or American? A re-examination of the transatlantic influence over the IMF},
  pdfkeywords={IMF, US hegemony, Europe},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{European or American? A re-examination of the transatlantic
influence over the IMF}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{GV499 Dissertation}
\author{Dianyi Yang~\orcidlink{0009-0004-4652-3429}\textsuperscript{}}
\date{2024-01-06}

\begin{document}
\maketitle
\begin{abstract}
This is an abstract.
\end{abstract}
\begin{center}
\keywords{IMF, US hegemony, Europe}
\end{center}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, breakable, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The International Monetary Fund (IMF) and the World Bank\footnote{Familar
  name for the International Bank for Reconstruction and Development
  (IBRD), the lending arm of the later created World Bank Group.} were
established toward the end of World War II as part of the Bretton Woods
agreement in 1944 (\protect\hyperlink{ref-jensen2004}{Jensen, 2004}).
While the World Bank specialised in long-term project financing, the IMF
was initially designed for addressing the short-term balance-of-payment
crises which would otherwise undermine the fixed exchange rate
arrangements under the Bretton Woods system
(\protect\hyperlink{ref-jensen2004}{Jensen, 2004}).

One renowned fact about the IMF and its sister institution, the World
Bank, is the long-standing ``gentlemen's agreement'' of the IMF managing
director being a European, and the World Bank president being an
American (\protect\hyperlink{ref-Keating2024}{Keating, 2024};
\protect\hyperlink{ref-Weiss2023}{Weiss, 2023}), despite no such
provisions in either institution's articles of agreements
(\protect\hyperlink{ref-Fund2020}{IMF, 2020};
\protect\hyperlink{ref-WorldBank2021}{World Bank, 2021}).

Such arrangements inspire a straightforward question that is yet
difficult to answer: who has more influence over the IMF, the US or
Europe? Whereas the US dominance in the World Bank is undisputed
(\protect\hyperlink{ref-clark2020}{Clark \& Dolan, 2020};
\protect\hyperlink{ref-wade2002}{Wade, 2002};
\protect\hyperlink{ref-woods2003}{Woods, 2003}), the case of the IMF is
much more complicated. As the
\protect\hyperlink{sec-litreview}{Literature Review} section
demonstrates, there has been abundant evidence of both European and
American influence on the IMF, but short of a qualitative or
quantitative comparison between the two.

Qualitative attempts at this question may have been thwarted by the
closed-door and consensus-based style of governance of the IMF, as
epitomised by the ``gentlemen's agreement''. On the one hand, the
frequent use of conventions and consensus renders any analyses on the
formal structure of the IMF (e.g.~veto power) insufficient on its own.
On the other hand, the closed-door negotiations imply that we often
observe the outcome, but not the process of the bargaining. While
specific case studies (e.g.~Mexico and European debt crisis, see Lipscy
\& Lee (\protect\hyperlink{ref-lipscy2018}{2018}) and Hodson
(\protect\hyperlink{ref-hodson2014}{2014})) may have shed light on the
influence of the US or Europe, they rarely allow for a transatlantic
comparison and their representativeness can be questioned.

@@

\hypertarget{sec-litreview}{%
\section{Literature Review}\label{sec-litreview}}

\begin{itemize}
\tightlist
\item
  IMF chief European (\protect\hyperlink{ref-Kahler2001}{Kahler, 2001})
\end{itemize}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-clark2020}{}}%
Clark, R., \& Dolan, L. R. (2020). Pleasing the Principal: U.S.
Influence in World Bank Policymaking. \emph{American Journal of
Political Science}, \emph{65}(1), 36--51.
\url{https://doi.org/10.1111/ajps.12531}

\leavevmode\vadjust pre{\hypertarget{ref-hodson2014}{}}%
Hodson, D. (2014). The IMF as a de facto institution of the EU: A
multiple supervisor approach. \emph{Review of International Political
Economy}, \emph{22}(3), 570--598.
\url{https://doi.org/10.1080/09692290.2014.956136}

\leavevmode\vadjust pre{\hypertarget{ref-Fund2020}{}}%
IMF. (2020). \emph{{Articles} of {Agreement}}. International Monetary
Fund.

\leavevmode\vadjust pre{\hypertarget{ref-jensen2004}{}}%
Jensen, N. M. (2004). Crisis, Conditions, and Capital. \emph{Journal of
Conflict Resolution}, \emph{48}(2), 194--210.
\url{https://doi.org/10.1177/0022002703262860}

\leavevmode\vadjust pre{\hypertarget{ref-Kahler2001}{}}%
Kahler, M. (2001). \emph{Leadership selection in the major
multilaterals}. Institute for International Economics.

\leavevmode\vadjust pre{\hypertarget{ref-Keating2024}{}}%
Keating, J. E. (2024). Why {Is} the {IMF} {Chief} {Always} a {European}?
In \emph{Foreign Policy}.
\url{https://foreignpolicy.com/2011/05/18/why-is-the-imf-chief-always-a-european/}

\leavevmode\vadjust pre{\hypertarget{ref-lipscy2018}{}}%
Lipscy, P. Y., \& Lee, H. N.-K. (2018). The IMF As a Biased Global
Insurance Mechanism: Asymmetrical Moral Hazard, Reserve Accumulation,
and Financial Crises. \emph{International Organization}, \emph{73}(1),
35--64. \url{https://doi.org/10.1017/s0020818318000371}

\leavevmode\vadjust pre{\hypertarget{ref-wade2002}{}}%
Wade, R. H. (2002). US hegemony and the World Bank: the fight over
people and ideas. \emph{Review of International Political Economy},
\emph{9}(2), 215--243. \url{https://doi.org/10.1080/09692290110126092}

\leavevmode\vadjust pre{\hypertarget{ref-Weiss2023}{}}%
Weiss, M. A. (2023). Selecting the world bank president. In
\emph{Congressional Research Service}.
\url{https://sgp.fas.org/crs/row/R42463.pdf}

\leavevmode\vadjust pre{\hypertarget{ref-woods2003}{}}%
Woods, N. (2003). \emph{The united states and the international
financial institutions: Power and influence within the world bank and
the IMF} (pp. 92--114). Oxford University PressOxford.
\url{https://doi.org/10.1093/0199261431.003.0005}

\leavevmode\vadjust pre{\hypertarget{ref-WorldBank2021}{}}%
World Bank. (2021). \emph{Articles of agreement}.
\url{https://www.worldbank.org/en/about/articles-of-agreement}

>>>>

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[top=30mm,left=30mm,right=30mm,heightrounded]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

% TODO: Add custom LaTeX header directives here
\usepackage{float, booktabs, siunitx, orcidlink}
\setkomafont{disposition}{\bfseries}
\providecommand{\keywords}[1]
{
  \small	
  \textbf
{\textit{Keywords---}} #1
}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={European or American? A re-examination of the transatlantic influence over the IMF},
  pdfkeywords={IMF, US hegemony, Europe},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{European or American? A re-examination of the transatlantic
influence over the IMF}
\author{Dianyi Yang~\orcidlink{0009-0004-4652-3429}\textsuperscript{}}
\date{2025-04-22}

\begin{document}
\maketitle
\begin{abstract}
This is an abstract.
\end{abstract}
\begin{center}
\keywords{IMF, US hegemony, Europe}
\end{center}

@@

\section{Introduction}\label{introduction}

The International Monetary Fund (IMF) and the World Bank\footnote{Familar
  name for the International Bank for Reconstruction and Development
  (IBRD), the lending arm of the later created World Bank Group.} were
established toward the end of World War II as part of the Bretton Woods
agreement in 1944 (\citeproc{ref-jensen2004}{Jensen, 2004}). While the
World Bank specialised in long-term project financing, the IMF was
initially designed for addressing the short-term balance-of-payment
crises which would otherwise undermine the fixed exchange rate
arrangements under the Bretton Woods system
(\citeproc{ref-jensen2004}{Jensen, 2004}).

One renowned fact about the IMF and its sister institution, the World
Bank, is the long-standing ``gentlemen's agreement'' of the IMF managing
director being a European, and the World Bank president being an
American (\citeproc{ref-Keating2024}{Keating, 2024};
\citeproc{ref-Weiss2023}{Weiss, 2023}), despite no such provisions in
either institution's articles of agreements
(\citeproc{ref-Fund2020}{IMF, 2020}; \citeproc{ref-WorldBank2021}{World
Bank, 2021}).

Such arrangements inspire a straightforward question that is yet
difficult to answer: who has more influence over the IMF, the US or
Europe? Whereas the US dominance in the World Bank is undisputed
(\citeproc{ref-clark2020}{Clark \& Dolan, 2020};
\citeproc{ref-wade2002}{Wade, 2002}; \citeproc{ref-woods2003}{Woods,
2003}), the case of the IMF is much more complicated. As the
\hyperref[sec-litreview]{Literature Review} section demonstrates, there
has been abundant evidence of both European and American influence on
the IMF, but short of a qualitative or quantitative comparison between
the two.

Qualitative attempts at this question may have been thwarted by the
closed-door and consensus-based style of governance of the IMF, as
epitomised by the ``gentlemen's agreement''. On the one hand, the
frequent use of conventions and consensus renders any analyses on the
formal structure of the IMF (e.g.~veto power) insufficient on its own.
On the other hand, the closed-door negotiations imply that we often
observe the outcome, but not the process of the bargaining. While
specific case studies (e.g.~Mexico and European debt crisis, see Lipscy
\& Lee (\citeproc{ref-lipscy2018}{2018}) and Hodson
(\citeproc{ref-hodson2014}{2014})) may have shed light on the influence
of the US or Europe, they rarely allow for a transatlantic comparison
and their representativeness can be questioned.

@@

\section{Literature Review}\label{sec-litreview}

\begin{itemize}
\tightlist
\item
  IMF chief European (\citeproc{ref-Kahler2001}{Kahler, 2001})
\end{itemize}

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-clark2020}
Clark, R., \& Dolan, L. R. (2020). Pleasing the Principal: U.S.
Influence in World Bank Policymaking. \emph{American Journal of
Political Science}, \emph{65}(1), 36--51.
\url{https://doi.org/10.1111/ajps.12531}

\bibitem[\citeproctext]{ref-hodson2014}
Hodson, D. (2014). The IMF as a de facto institution of the EU: A
multiple supervisor approach. \emph{Review of International Political
Economy}, \emph{22}(3), 570--598.
\url{https://doi.org/10.1080/09692290.2014.956136}

\bibitem[\citeproctext]{ref-Fund2020}
IMF. (2020). \emph{{Articles} of {Agreement}}. International Monetary
Fund.

\bibitem[\citeproctext]{ref-jensen2004}
Jensen, N. M. (2004). Crisis, Conditions, and Capital. \emph{Journal of
Conflict Resolution}, \emph{48}(2), 194--210.
\url{https://doi.org/10.1177/0022002703262860}

\bibitem[\citeproctext]{ref-Kahler2001}
Kahler, M. (2001). \emph{Leadership selection in the major
multilaterals}. Institute for International Economics.

\bibitem[\citeproctext]{ref-Keating2024}
Keating, J. E. (2024). Why {Is} the {IMF} {Chief} {Always} a {European}?
In \emph{Foreign Policy}.
\url{https://foreignpolicy.com/2011/05/18/why-is-the-imf-chief-always-a-european/}

\bibitem[\citeproctext]{ref-lipscy2018}
Lipscy, P. Y., \& Lee, H. N.-K. (2018). The IMF As a Biased Global
Insurance Mechanism: Asymmetrical Moral Hazard, Reserve Accumulation,
and Financial Crises. \emph{International Organization}, \emph{73}(1),
35--64. \url{https://doi.org/10.1017/s0020818318000371}

\bibitem[\citeproctext]{ref-wade2002}
Wade, R. H. (2002). US hegemony and the World Bank: the fight over
people and ideas. \emph{Review of International Political Economy},
\emph{9}(2), 215--243. \url{https://doi.org/10.1080/09692290110126092}

\bibitem[\citeproctext]{ref-Weiss2023}
Weiss, M. A. (2023). Selecting the world bank president. In
\emph{Congressional Research Service}.
\url{https://sgp.fas.org/crs/row/R42463.pdf}

\bibitem[\citeproctext]{ref-woods2003}
Woods, N. (2003). \emph{The united states and the international
financial institutions: Power and influence within the world bank and
the IMF} (pp. 92--114). Oxford University PressOxford.
\url{https://doi.org/10.1093/0199261431.003.0005}

\bibitem[\citeproctext]{ref-WorldBank2021}
World Bank. (2021). \emph{Articles of agreement}.
\url{https://www.worldbank.org/en/about/articles-of-agreement}
